---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# maxk

<!-- badges: start -->
<!-- badges: end -->

The goal of maxk is to provide interfaces like getting the k-th largest element in a vector with two parameters, `nums` and `k` on a 1-index basis, etc.

## Installation

maxk is not yet on CRAN. But, you can download it from this repository using the following R command:


``` r
devtools::install_github("stat545ubc-2021/maxk")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(maxk)
kth_largest_element(c(5,4,8,7,1), 2)
```

The function finds the second largest element in the vector, which is 7, and returns it.

This package is special because it also works with an invalid `k`:

```{r}
kth_largest_element(c(5,4,8,7,1), -1)
```

Here apparently -1 is not valid, but it is treated as 1. The function still gets the largest element in the vector, which is 8.

```{r}
kth_largest_element(c(5,4,8,7,1), 6)
```

Similarly, 6 is not valid, but it is treated as 5 (the length of the vector). The function still gets the fifth largest element in the vector, which is 1.

For now, the function only supports numeric vector input, character input or empty input will throw errors.

```{r, error=TRUE}
kth_largest_element(c('a', 'b', 'c'), 6)

kth_largest_element(c(), 5)
```
